### 2013-09-17 chi2014/summary.tex
fixed an error where repeat workers were counted towards cluster size

\begin{table}
	\begin{tabular}[h!]{r | l l l l l l l}
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline \hline
	HITs & 57 & 47 & 23 & 10 & 10 & 10 & 146\\
	instances & 293 & 471 & 453 & 500 & 634 & 855 & 3007\\
	ideas & 171 & 249 & 278 & 341 & 443 & 177 &1212\\
	category trees & 76 & 93 & 100 & 123 & 172 & 177 &321\\
	non-singleton trees & 28 & 41 & 41 & 50 & 49 & 61 &92\\
	\end{tabular}
\end{table}

@@

\begin{table}
	\begin{tabular}[h!]{r | l l l l l l l}
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline \hline
	median & 2 & 2 & 2 & 2 & 2 & 2 & 1\\
	first quartile & 2 & 1  & 1 & 1 & 1 & 1 & 1\\
	third quartile & 2 & 3 &3 &3 &2 &2 & 2\\
	\end{tabular}
	\caption{Category tree height}
\end{table}

@@

\begin{table}
\begin{tabular}[h!]{r | l l l l l l l}
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline \hline
	number of nodes& \\ \hline
	median &3&4&4&3&2&2&1 \\
	first quartile &2&1&1&1&1&1&1 \\
	third quartile &15&12&12&10&5&5&3 \\
	number of instances& \\ \hline
	median &14&12&12&9&4&4&2 \\
	first quartile &4&3&4&2&1&1&1 \\
	third quartile &48&31&29&21&14&13&6 \\
	\end{tabular}
	\caption{Number of ideas and instances in trees}
\end{table}

>>>>

\begin{table}
	\begin{tabular}[h!]{r | l l l l l l l}
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline \hline
	HITs & 57 & 47 & 23 & 10 & 10 & 10 & 146\\
	instances & 293 & 471 & 453 & 500 & 634 & 855 & 3007\\
	ideas & 171 & 249 & 278 & 341 & 443 & 177 &1212\\
	category trees & 72 & 79 & 93 & 114 & 172 & 177 &321\\
	non-singleton trees & 28 & 34 & 40 & 48 & 49 & 61 &92\\
	\end{tabular}
\end{table}

@@

\begin{table}
	\begin{tabular}[h!]{r | l l l l l l l}
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline \hline
	median & 2 & 2 & 2 & 2 & 2 & 2 & 2\\
	first quartile & 2 & 2  & 1 & 1 & 1 & 1 & 1\\
	third quartile & 3 & 3 &3 &3 &2 &2 & 2\\
	\end{tabular}
	\caption{Category tree height}
\end{table}

@@

\begin{table}
\begin{tabular}[h!]{r | l l l l l l l}
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline \hline
	number of nodes& \\ \hline
    median &5&5&4&3&2&2&2 \\
	first quartile &2&2&1&1&1&1&1 \\
	third quartile &17&17&14&10&5&5&5 \\
	number of instances& \\ \hline
	median &14&14&12&10&4&4&4 \\
    first quartile &4&4&4&2&1&1&1 \\
	third quartile &47&45&30&23&13&13&13 \\
	\end{tabular}
	\caption{Number of ideas and instances in trees}
\end{table}
